\chapter{The master inequality: extension to smooth functions}

The aim of this chapter is to prove the Master inequality II, as
done in \cite[Section 7]{chen2025}.
This will require to prove some results related to approximations
of smooth functions by Chebyshev polynomials on a compact set.

Throughout the rest of this blueprint,
we will denote as $\tor = \R / 2 \pi\Z$ the additive circle of length $2 \pi$.

\section{Chebyshev polynomials}

For $j \geq 0$, we denote as $T_j$ the Chebyshev polynomial of the first kind of degree $j$,
defined by the relation $T_j(\cos \theta) = \cos(j \theta)$ for $\theta \in \R$.

Let us fix a real number $K > 0$ and an integer $q \geq 0$ for this section.
We define coefficients associated to a polynomial $h$ on the set $[-K,K]$ in the following
fashion.

\begin{lemma}
  \label{lem:chebyshev_decomp}
  Let $h \in \mathcal{P}_q$.
  There exists a unique family of real numbers $(a_j)_{0 \leq j \leq q}$ such that,
  for all $x \in \R$,
  \begin{equation*}
    h(Kx) = \sum_{j=0}^q a_j T_j (x).
  \end{equation*}
\end{lemma}

\begin{proof}
  This follows from the fact that $h(Kx) \in \mathcal{P}_q$ and $(T_j)_{0 \leq j \leq q}$ is a basis of $\mathcal{P}_q$,
  since for all $0 \leq j \leq q$, $\deg T_j = j$.
\end{proof}

It will be useful to view the coefficients $(a_j)_{0 \leq j \leq q}$ as trigonometric
Fourier coefficients, which we do by introducing the following function $f$.

\begin{lemma}
  \label{lem:f_def}
  \uses{lem:chebyshev_decomp}
  Let $h \in \mathcal{P}_q$ and $(a_j)_{0 \leq j \leq q}$ be the coefficients from Lemma
  \ref{lem:chebyshev_decomp}.
  Let $f : \tor \rightarrow \R$ be the function defined by $f(\theta) = h(K \cos \theta)$.
  Then, $f$ is an even trigonometric polynomial equal to
  \begin{equation*}
    f(\theta)
    =
      \sum_{j=0}^q a_j \cos(j \theta).
 \end{equation*}
\end{lemma}

\begin{proof}
  By definition of $f$ and $(a_j)_{0 \leq j \leq q}$,
  for all $\theta \in \tor$,
  \begin{equation*}
    f(\theta) = h(K \cos \theta) = \sum_{j=0}^q a_j T_j(\cos \theta).
  \end{equation*}
  By definition of $(T_j)_{j \geq 0}$, $T_j(\cos \theta) = \cos (j \theta)$.
  The evenness comes from the fact that $\cos$ is even.
\end{proof}

We will now provide some bounds on the coefficients $(a_j)_{0 \leq j \leq q}$
in terms of $L^\beta$-bounds on derivatives of $f$.
Recall that, for a function $f \in L^1(\tor)$ and an integer $j \in \Z$,
the $j$-th Fourier coefficient is defined as
\begin{equation*}
  c_j = \frac{1}{2 \pi} \int_0^{2 \pi} f(\theta) e^{-i j \theta} \d \theta.
\end{equation*}

\begin{lemma}
  \label{lem:coeff_of_f}
  Let $f(\theta) = \sum_{j=0}^q a_j \cos(j \theta)$ be an even trigonometric series.
  Then, the Fourier coefficients of $f$ are exactly, for $j \in \Z$,
  $c_j = \frac{1}{2} a_{|j|}$ if $0 < |j| \leq q$, $a_0$ if $j=0$ and $0$ if $|j|>q$.
\end{lemma}

\begin{proof}
  This is probably already in Mathlib.
\end{proof}


\begin{lemma}
  \label{lem:bound_a0}
  \uses{lem:f_def,lem:coeff_of_f}
  Let $h \in \mathcal{P}_q$ and $(a_j)_{0 \leq j \leq q}$ be the coefficients from Lemma
  \ref{lem:chebyshev_decomp}.
  Then,
  \begin{equation*}
    |a_0| \leq \| h \|_{C^0[-K,K]}.
  \end{equation*}
\end{lemma}

\begin{proof}
  By Lemma \ref{lem:f_def} and \ref{lem:coeff_of_f}, we have
  \begin{equation*}
    a_0 = c_0 = \frac{1}{2 \pi} \int_0^{2 \pi} f(\theta) \d \theta.
  \end{equation*}
  Hence by the triangle inequality
  \begin{equation*}
    |a_0| \leq \frac{1}{2 \pi} \int_0^{2 \pi} |f(\theta)| \d \theta
    = \frac{1}{2 \pi} \int_0^{2 \pi} |h(K \cos \theta)| \d \theta
    \leq \| h \|_{C^0[-K,K]}.
  \end{equation*}
\end{proof}

The following bound relies on the Hausdorff-Young inequality, which is a classic result.

\begin{theorem}
  \label{thm:hausdorff_young}
  Let $1 < \beta \leq 2$ and $1/\beta_* = 1 - 1/\beta$.
  Let $f \in L^\beta(\tor)$ of Fourier coefficients $(c_j)_{j \in \Z}$.
  Then,
  \begin{equation*}
    \left(\sum_{j \in \Z} |c_j|^{\beta_*} \right)^{1/\beta_*}
    \leq \left(\frac{1}{2 \pi} \int_0^{2 \pi} |f(\theta)|^\beta \d \theta\right)^{1/\beta}.
  \end{equation*}
\end{theorem}

\begin{proof}
  I think this might be in Mathlib? If not this is a classic result and should be added.
  This is proven by interpolation between Parseval and the $L^\infty$-$L^1$ trivial estimate,
  using Riesz-Thorin.
\end{proof}

We deduce the following lemma.

\begin{lemma}
  \label{lem:Zygmund}
  \uses{thm:hausdorff_young}
  Let $\beta > 1$ and $1/\beta_* = 1-1/\beta$.
  Let $f \in L^1(\tor)$ of Fourier coefficients $(c_j)_{j \in \Z}$.
  Assume $f' \in L^\beta(\tor)$.
  Then,
  \begin{equation*}
    \sum_{j \neq 0} |c_j| \leq 4 \beta_* \|f' \|_{L^\beta(\tor)}.
  \end{equation*}
\end{lemma}

\begin{proof}
  Assume $1 < \beta \leq 2$.
  By the H\"older inequality,
  \begin{equation*}
    \sum_{j \neq 0} |c_j|
    = \sum_{j \neq 0} \frac{1}{|j|} \times |j c_j|
    \leq
    \left(\sum_{j \neq 0} \frac{1}{|j|^\beta} \right)^{1/\beta}
    \left(\sum_{j \neq 0} |j c_j|^{\beta_*} \right)^{1/\beta_*}.
  \end{equation*}
  We shall bound these two sums successively.
  \begin{itemize}
    \item   Since $\beta>1$ the first sum converges. By parity it is equal to twice the sum for $j \geq 1$.
  Since $t \mapsto 1/t^\beta$
  is decreasing on $[1,\infty)$, we can compare the sum and integral which yields
  \begin{equation*}
    \sum_{j =1}^\infty \frac{1}{j^\beta}
    \leq 1 + \int_1^\infty \frac{\d t}{t^\beta}
    = 1 - \left[ \frac{1}{(\beta-1)t^{\beta-1}} \right]_1^\infty
    = 1 + \frac{1}{\beta - 1}
    = \frac{\beta}{\beta - 1} = \frac{1}{1 - 1/\beta} = \beta_*.
  \end{equation*}
  As a conclusion,
  \begin{equation*}
    \left(\sum_{j \neq 0} \frac{1}{|j|^\beta} \right)^{1/\beta}
    \leq 2 \beta_*^{1/\beta} \leq 2 \beta_*
  \end{equation*}
  since $0 \leq 1/\beta \leq 1$ and $\beta_* \geq 1$.
  \item For the second sum, we observe that the Fourier coefficients of $f'$
  are $(i j c_j)_{j \in \Z}$. Since $1 < \beta \leq 2$, we can
  apply Theorem \ref{thm:hausdorff_young} to $f'$, which yields
  \begin{equation*}
    \left(\sum_{j \neq 0} |j c_j|^{\beta_*} \right)^{1/\beta_*}
    \leq
    \left(\frac{1}{2 \pi} \int_0^{2 \pi} |f'(\theta)|^\beta \d \theta\right)^{1/\beta}
    \leq \frac{1}{(2 \pi)^{1/\beta}} \|f'\|_{L^\beta(\tor)}
    \leq \frac{1}{\sqrt{2 \pi}} \|f'\|_{L^\beta(\tor)}
  \end{equation*}
  since $\beta \leq 2$.
  \end{itemize}
  Putting everything together we obtain
  \begin{equation*}
    \sum_{j \neq 0} |c_j|
    \leq \sqrt{\frac{2}{\pi}} \beta_*  \|f'\|_{L^\beta(\tor)}
  \end{equation*}
  which implies the claim in the case $1 < \beta \leq 2$ since $\sqrt{2/\pi} \leq 4$.

  Now assume $\beta \geq 2$.
  By the H\"older inequality, since $\tor$ has finite measure $2 \pi$,
  $L^\beta(\tor) \subseteq L^2(\tor)$ and
  \begin{equation*}
    \|f'\|_{L^2(\tor)}^2
   \leq  \left(\int_0^{2 \pi} 1 \d \theta\right)^{1-\frac{2}{\beta}}
    \left(\int_0^{2 \pi} |f'(\theta)|^{\beta} \d \theta\right)^{\frac{2}{\beta}}
    = (2 \pi)^{1-\frac{2}{\beta}}  \|f'\|_{L^\beta(\tor)}^2
    \leq 2 \pi \|f'\|_{L^\beta(\tor)}^2.
  \end{equation*}
  In particular, we can apply the result for $\beta=2$ (in which case $\beta_*=2$),
  which yields
  \begin{equation*}
    \sum_{j \neq 0} |c_j|
    \leq 2 \sqrt{\frac{2}{\pi}}  \|f'\|_{L^2(\tor)}
    \leq 4 \|f'\|_{L^\beta(\tor)}
    \leq 4 \beta_*  \|f'\|_{L^\beta(\tor)}
  \end{equation*}
  since $\beta_* \geq 1$.
\end{proof}

We now conclude with the main result of this section.

\begin{lemma}
  \label{lem:bound_sum_aj}
  \uses{lem:Zygmund,lem:coeff_of_f,lem:f_def}
  Let $h \in \mathcal{P}_q$, and $f$ and $(a_j)_{0 \leq j \leq q}$ be as in Lemma \ref{lem:f_def}.
  For any $m \geq 0$,
  any $\beta > 1$, if we denote $1/\beta_* := 1 - 1/\beta$, we have
  \begin{equation*}
    \sum_{j=1}^q j^m |a_j| \leq 4 \beta_* \|f^{(m+1)}\|_{L^\beta(\tor)}.
  \end{equation*}
\end{lemma}

\begin{proof}
  First, we apply Lemma \ref{lem:coeff_of_f} to express the Fourier coefficients
  $(c_j)_{j \in \Z}$ in terms of $(a_j)_{0 \leq j \leq q}$.
  Let $m \geq 0$. By differentiation,
  the Fourier coefficients of $f^{(m)}$ satisfy, for
  all $j$, $c_j^{(m)} =
    i^m j^m c_j$.
  In particular,
  \begin{equation*}
    \sum_{j \neq 0} |c_j^{(m)}|
    = \sum_{j \neq 0} |j|^m |c_j|
    = \sum_{j =1}^q j^m |a_j|.
  \end{equation*}
  The conclusion follows by applying Lemma \ref{lem:Zygmund} to the function $f^{(m)}$,
  of derivative $f^{(m+1)}$ in $L^\beta(\tor)$ as it is a trigonometric polynomial and in particular smooth.
\end{proof}

We shall use the following corollary.

\begin{corollary}
  \label{coro:bound_sum_aj}
  \uses{lem:bound_sum_aj}
  Let $m \geq 0$ be an integer and $K > 0$ be a real number.
  There exists a real number $c_{m,K}$ satisfying the following.
  For any $q \geq 1$, any
  $h \in \mathcal{P}_q$, if $(a_j)_{0 \leq j \leq q}$ are
  the coefficients from Lemma \ref{lem:chebyshev_decomp},
  then
  \begin{equation*}
    \sum_{j=1}^q j^m |a_j| \leq c_{m,K} \|h\|_{C^{m+1}([-K,K])}.
  \end{equation*}
\end{corollary}

\begin{proof}
  We apply Lemma \ref{lem:bound_sum_aj} with $\beta = \infty$, in which case $\beta_*=1$
  and hence $$\sum_{j=1}^q j^m |a_j| \leq 4 \|f^{(m+1)}\|_{L^\infty(\tor)}.$$
  We then use the chain rule to find a constant $C_{m,K}$ such that
  $\|f^{(m+1)}\|_{L^\infty(\tor)} \leq C_{m,K} \|h\|_{C^{m+1}([-K,K])}$
  and conclude with $c_{m,K}=4C_{m,K}$.
\end{proof}

\section{Compactly supported distributions}

In this section, we will prove a few useful elementary results on distributions.

\subsection{Support of a distribution}

Let $\Omega$ be an open subset of a real finite-dimensional normed space $E$
and $F$ be a real locally convex topological vector space.

We denote as $\smooth[\Omega, F]$ the space of smooth functions $\Omega \rightarrow F$, and
$\testfunc[\Omega, F]$
the set of smooth functions $\Omega \rightarrow F$ with compact support.
For $h \in \testfunc[\Omega, F]$, we denote as $\supp h$ its support.
For $K$ a compact subset of $\Omega$ and $h \in \testfunc[\Omega, F]$, we write
\begin{equation*}
  \|h\|_{C^m(K)} = \sup_{0 \leq k \leq m} \sup_{x \in K} |h^{(k)}(x)|
\end{equation*}
where $h^{(k)}$ is the $k$-th order derivative of $h$.
We denote as $\distrib[\Omega, F]$ the space of classical distributions, i.e. continuous
linear functionals $\nu : \testfunc[\Omega, F] \rightarrow F$.
Here continuous means that, for any compact $K$ of $\Omega$,
there exists a constant $C \geq 0$ and an integer $m \geq 0$ (both depending on $K$) such that
\begin{equation*}
  \forall h \in \testfunc[\Omega,F], \quad
  \supp h \subseteq K \Rightarrow  |\nu(h)| \leq C \|h\|_{C^m(K)}.
\end{equation*}

We recall the definition of support, which should be added quite soon to Mathlib.

\begin{definition}
  \label{def:distribution_vanishes}
  Let $A$ be a subset of $\Omega$. We say $\nu \in \distrib[\Omega, F]$ \emph{vanishes on} $A$
  if, for all $h \in \testfunc[\Omega, F]$, if $\supp h \subseteq A$, then $\nu(h)=0$.
\end{definition}

\begin{definition}
  \label{def:support_distribution}
  \uses{def:distribution_vanishes}
  Let $\nu \in \distrib[\Omega, F]$.
  The \emph{support} of $\nu$ is the intersection of all closed sets $A \subseteq \R$
  such that $\nu$ vanishes on the complement of $A$. We denote it as $\supp \nu$.
\end{definition}

\subsection{Characterisation of compactly supported distributions}

\begin{definition}
  \label{def:compactly_supported_distribution}
  \uses{def:support_distribution}
  Let $\csdistrib[\Omega,F]$ be the set of \emph{compactly supported distribution}
  i.e. linear functionals $\nu : \smooth[\Omega,F] \rightarrow F$
  such that there exists a compact set $K \subset \Omega$, a real number $C$
  and an integer $m\geq 0$ such that,
  for all $h \in \smooth[\Omega,F]$,
  $|\nu(h)| \leq C \|h\|_{C^m(K)}$.
\end{definition}

\begin{lemma}
  \label{lem:E_implies_CS}
  \uses{def:compactly_supported_distribution}
  Let $\nu \in \csdistrib[\Omega,F]$, and let $K$, $C$, $m$ be as in Definition
  \ref{def:compactly_supported_distribution}.
  Then the restriction of $\nu$ to $\testfunc[\Omega,F]$ is an element of
  $\distrib[\Omega,F]$, and its support is included in $K$.
\end{lemma}

\begin{proof}
  We first prove that the restriction is an element of $\distrib[\Omega,F]$.
  By definition, for all $h \in \smooth[\Omega,F]$, we have
  $|\nu(h)| \leq C \|h\|_{C^m(K)}$, with $K$, $C$, $m$ as in the statement.
  Now take $K'$ a compact set of $\Omega$.
  Let $h \in \testfunc[\Omega,F]$ such that $\supp h \subset K'$.
  In particular, $h \in \smooth[\Omega,F]$, so we have $|\nu(h)| \leq C \|h\|_{C^m(K)}$.
  But since $h$ is identically equal to $0$ outside of $K'$, $\|h\|_{C^m(K)} \leq \|h\|_{C^m(K')}$,
  which is what we needed to prove.

  Now to prove the support claim, let us prove that $\nu$ vanishes on $K^c$, ie
  for all $h \in \testfunc[\Omega,F]$ such that $\supp h \subseteq K^c$,
  we have $\nu(h)=0$. Indeed, for such a $h$,
  we have $|\nu(h)| \leq C \|h\|_{C^m(K)}$. But $\|h\|_{C^m(K)} = 0$ since $h$
  is identically equal to $0$ on $K$, and hence $\nu(h)=0$.
  Hence, the support of $\nu$ is included in $K$. Since the support is closed
  and $K$ is compact, $\supp \nu$ is compact.
\end{proof}

We here prove that $\csdistrib[\Omega, F]$ is the space of elements of $\distrib[\Omega,F]$
with compact support, which justifies the name.

\begin{lemma}
  \label{lem:Leibniz}
  Let $\phi \in \testfunc[\Omega,F]$. Then, for any $h \in \smooth[\Omega,F]$,
  the product $\phi h$ belongs in $\testfunc[\Omega,F]$
  and $\supp (\phi h) \subseteq \supp (\phi)$.
  Furthermore, for any compact set $K$ of $\Omega$, any integer $m \geq 0$,
  there exists a constant $C$ (depending on $\phi$)
  such that,
  for all $h \in \smooth[\Omega,F]$, $\|\phi h\|_{C^m(K)} \leq C \|h\|_{C^m(K)}$.
\end{lemma}

\begin{proof}
  This follows from Leibniz's formula.
\end{proof}

\begin{lemma}
  \label{lem:extension_csd}
  \uses{def:compactly_supported_distribution,lem:Leibniz}
  Let $\nu \in \distrib[\Omega, F]$. We assume that $\supp \nu$ is compact.
  Then there is a unique $\mu \in \csdistrib[\Omega,F]$
  such that, for all $h \in \testfunc[\Omega,F]$,
  $\nu(h)=\mu(h)$.
\end{lemma}

\begin{proof}
  The support of $\nu$ is compact, we denote it as $K_0$.
  We take a function $\phi \in \testfunc[\Omega,F]$
  such that $\phi$ is identically equal to
  $1$ on $K_0$.
  We then define $\mu : \smooth[\Omega,F] \rightarrow F$
  by letting $\mu(h) := \nu(h \phi)$ for $h \in \smooth[\Omega,F]$.
 \begin{itemize}
  \item  This is well-defined by Lemma \ref{lem:Leibniz}. The linearity is immediate.
  \item We prove that $\mu$ is an extension of $\nu$.
  Let $h \in \testfunc[\Omega,F]$.
  We observe that $(1-\phi) h$ belongs in $\testfunc[\Omega,F]$ and
  is identically equal to $0$ on $K_0 = \supp \nu$.
  This implies (by a simple lemma on supports) that $\nu((1-\phi)h) = 0$,
  hence $\nu(h) = \nu(\phi h) = \mu(h)$.
  \item Let us now prove the norm estimate for $\mu$.
\begin{itemize}
  \item
  The function $\phi$ has compact support, which we denote by $K$.
  By definition of $\distrib[\Omega,F]$ applied to $K$, we obtain a constant $C_1$
  and an integer $m$ such that, for all $h \in \testfunc[\Omega,F]$,
  if $\supp h$ is included in $K$, then
  we have $|\nu(h)| \leq C_1 \|h\|_{C^m(K)}$.
 \item Lemma \ref{lem:Leibniz} grants a constant $C_2$ (depending on $\phi$) such that,
 for all $h \in \smooth[\Omega,F]$,
  $\|\phi h\|_{C^m(K)} \leq C_2 \|h\|_{C^m(K)}$.
\end{itemize}
Now take $h \in \smooth[\Omega,F]$.
By Lemma \ref{lem:Leibniz}, $\phi h \in \testfunc[\Omega,F]$ and its support is included in
$K$. Hence,
\begin{equation*}
  |\mu(h)| = |\nu(\phi h)| \leq C_1 \|\phi h\|_{C^m(K)}.
\end{equation*}
We then note that $\|\phi h\|_{C^m(K)} \leq C_2 \|h\|_{C^m(K)}$.
This proves the claim with $C := C_1 C_2$.
\item  The uniqueness is then obtained by the density of $\testfunc[\Omega,F]$ in $\smooth[\Omega,F]$.
\end{itemize}
\end{proof}

This allows us to make sense of $\nu(h)$ for $\nu$ a compactly supported distribution
and $h$ a general smooth function, an essential component of the proof.

\subsection{Extension from polynomials to smooth functions}

It will be essential for us to extend linear operators acting on polynomials
to compactly supported distributions. The following proposition provides a criterium for this.

\begin{proposition}
  \label{prop:extension_poly_smooth}
  \uses{coro:bound_sum_aj,def:compactly_supported_distribution,prop:Markov_ineq}
  Let $\nu : \mathcal{P} \rightarrow \C$ be a linear functional.
  The following three properties are equivalent.
  \begin{enumerate}
    \item There exists $c, K, m \geq 0$ such that, for all $q \geq 1$, all
    $h \in \mathcal{P}_q$,
    \begin{equation*}
      |\nu(h)| \leq c q^m \|h\|_{C^0([-K,K])}.
    \end{equation*}
    \item There exists $c, K, m \geq 0$ such that, for all $j \geq 1$,
    \begin{equation*}
      |\nu(T_j(\cdot / K))| \leq c j^m.
    \end{equation*}
    \item $\nu$ extends uniquely to a compactly supported distribution.
  \end{enumerate}
\end{proposition}

\begin{proof}
  We will prove $1 \Rightarrow 2 \Rightarrow 3 \Rightarrow 1$.

  Let us assume $1$.
  Let $j \geq 1$.
  Let $h (x) := T_j(x/K)$.
  We note that $h$ is an element of $\mathcal{P}_j$, so can apply the
  hypothesis to it, which yields $|\nu(h)| \leq c j^m \|h\|_{C^0([-K,K])}$.
  We conclude by observing that $\|h\|_{C^0([-K,K])} = \|T_j\|_{C^0([-1,1])}=1$
  using the definition of the Chebyshev polynomials.

  Let us now assume $2$, which gives us some parameters $c, K, m$.
  Let $q \geq 1$ and $h \in \mathcal{P}_q$. We write $h = \sum_{j=0}^q a_j T_j(\cdot / K)$
  as before. Then by linearity, the triangle inequality and  the assumption
  \begin{equation*}
    |\nu(h)|
    \leq |a_0| |\nu(1)| + \sum_{j=1}^q |a_j| |\nu(T_j(\cdot / K))|
    \leq |a_0| |\nu(1)| + c \sum_{j=1}^q j^m|a_j|.
  \end{equation*}
  By Lemma \ref{lem:bound_a0}, $|a_0| \leq \|h\|_{C^0([-K,K])}$.
  By Corollary \ref{coro:bound_sum_aj}, there exists a constant $c_{m,K}$
  depending only on $m$ and $K$ such that
  $\sum_{j=1}^q j^m|a_j| \leq c_{m,K} \|h\|_{C^{m+1}([-K,K])}$.
  Then, taking $C := |\nu(1)| + c c_{m,K}$, we have that
  for all $h \in \mathcal{P}$,
  $|\nu(h)| \leq C \|h\|_{C^{m+1}([-K,K])}$.
  By density of $\mathcal{P}$ in $\smooth$
  for $\|\cdot \|_{C^{m+1}([-K,K])}$, $\nu$ extends uniquely to a compactly
  supported distribution.

  To conclude, we prove $3 \Rightarrow 1$. [todo]
\end{proof}

\section{Proof of the Master inequality II}

We can now proceed to the proof of second master inequality.

\begin{theorem}
  \label{thm:masterII}
  \uses{thm:masterI,prop:extension_poly_smooth,lem:bound_sum_aj,coro:masterI}
  Let $r \geq 2$ and $D \geq 1$.
  Fix a self-adjoint non-commutative polynomial $P \in \nonco$
  of degree $q_0$, and let $K = \|P\|_{D,r}$.
  There exists a family of compactly supported distributions $(\nu_i)_{i\geq 0}$
  satisfying the following.
  For any $\beta > 1$, $\frac{1}{\beta_*} + \frac{1}{\beta} = 1$,
  any $N,m \geq 1$, any $h \in \smooth$, if $f(\theta) := h(K\cos(\theta))$, then
  \begin{equation*}
    \left|\expec\left[\trN[ND] h(P(S_1, \ldots, S_r))\right]
     - \sum_{i=0}^{m-1} \frac{\nu_i(h)}{N^i}\right|
     \leq 4 \beta_* \frac{(4 q_0(1+\log r))^{4m}}{N^m} \|f^{(4m+1)}\|_{L^\beta(\tor)}.
  \end{equation*}
\end{theorem}

\begin{proof}
  Let $i \geq 0$.
  By Lemma \ref{coro:masterI},
  for every $q \geq 1$ and $h \in \mathcal{P}_q$,
  \begin{equation*}
    |\nu_i(h)|
    \leq c q^{4i} \|h\|_{C^0([-K,K])}.
  \end{equation*}
  where $c = (4 q_0(1+\log r))^{4i}$.
  By Proposition \ref{prop:extension_poly_smooth} ($3 \Rightarrow 1$)
  with $K$, $c$ and $m=4i$, $\nu_i$ can be uniquely extended to a compactly supported
  distribution.

  Let us now take $q \geq 1$ and $h \in \mathcal{P}_q$. [todo]
\end{proof}
