\chapter{Proof of Friedman's theorem}

\section{The free group and its reduced algebra}

\begin{definition}
  \label{def:free_group}
  We denote as $\free = \langle g_1, \ldots, g_r \rangle$ the \emph{free group} with $r$ generators.
\end{definition}

\section{Support of a real distribution}

\subsection{Stieltjes transform}

In this section we introduce a useful tool which will be essential to the next section.
Let $\RS$ denote the Riemann sphere.

\begin{lemma}
  \label{lem:Stieltjes_function}
  Let $z \in \RS$ such that $z \notin \R$.
  The function $x \in \R \mapsto \frac{1}{2i\pi} \frac{1}{x-z} \in \C$ is
  an element of $\smooth$.
\end{lemma}

\begin{proof}
  Usual functions.
\end{proof}

\begin{definition}
  \label{def:Stieltjes}
  \uses{lem:extension_csd,lem:Stieltjes_function}
  Let $\nu \in \csdistrib$.
  The \emph{Stieltjes transform} of $\nu$ is defined as the function
  $F_\nu : \RS - \R \rightarrow \C$ by $F(z) = \nu(x \mapsto \frac{1}{2 i \pi}\frac{1}{x-z})$.
\end{definition}

\begin{theorem}
  \label{thm:Stieltjes_boundary_values}
  \uses{lem:Stieltjes_function}
  \notready
  Let $\nu \in \csdistrib$.
  For any $h \in \smooth$,
  \begin{equation*}
    \nu(h)
    =
    \lim_{\epsilon \rightarrow 0^+}
    \int_{\R} (F_\nu(x+i \epsilon) - F_\nu(x - i \epsilon)) h(x) \d x.
  \end{equation*}
\end{theorem}

\begin{proof}
  This can be done by computing explicitely the values of $F_\nu(x \pm i \epsilon)$
  and seeing the resulting integral as an approximation of $\delta_x$ as $\epsilon \rightarrow 0^+$,
  [todo write the details].
\end{proof}

\begin{theorem}
  \label{thm:Stieltjes_holomorphic}
  \uses{thm:Stieltjes_boundary_values}
  \notready
  Let $\nu \in \csdistrib$.
  The function $F_\nu : \RS - \R \rightarrow \C$ is analytic.
  It can be analytically extended to a $x \in \R$ if and only if $x \notin \supp \nu$.
\end{theorem}

\begin{proof}
  This proof is not complete yet as it requires a bit of work on distributions.

  [todo: find a general result describing when $\nu(h(\cdot, z))$ is holomorphic, there is
  information on this in Mathematical Methods in Physics: Distributions, Hilbert Space Operators,
  Variational Methods, and Applications in Quantum Physics]

  [todo: write the details]

  For $z \in \R$, if $z \notin \supp(\nu)$, then we take a
  $\phi \in \testfunc$ such that $\phi$ is identically equal to $1$ on $\supp (\nu)$
  and identically equal to $0$ on a neighbourhood of $z$.
  We then observe that $x \in \R \mapsto  \frac{1}{2 i \pi} \frac{\phi(x)}{x-z}$
  is an element of $\smooth$ and hence we can
  define $\tilde{F}_\nu(z) = \nu(\frac{1}{2 i \pi} \frac{\phi(x)}{x-z})$.
  We check it is an extension of $F_\nu$ and analytic on a neighbourhood of $z$.

  Let $z \in \R$. We assume that $F_\nu$ admits an analytic extension on the ball of radius $r$
  centered at $z$.
  Let $r' \in (0,r)$ and
  $h \in \smooth$ such that $\supp(h) \subset [z-r',z+r']$.
  By Theorem \ref{thm:Stieltjes_boundary_values},
  \begin{equation*}
    \nu(h) = \lim_{\epsilon \rightarrow 0^+}
    \int_{z-r'}^{z+r'} (F_\nu(x+i \epsilon) - F_\nu(x - i \epsilon)) h(x) \d x.
  \end{equation*}
  For small enough $\epsilon>0$, and any $x \in [z-r',z+r']$,
  $F_\nu(x \pm i \epsilon)$ lies in the ball of radius $r$ around $z$ where $F_\nu$
  is analytically extended. We use this information to prove the that limit above (and hence
  $\nu(h)$) is equal to $0$. Since this holds for any $h$ supported on $[z-r',z+r']$,
  $z \notin \supp(h)$.
\end{proof}

\subsection{Spectral radius and support}

We shall now show how one can access the support of a distribution
from its moments.

\begin{lemma}
  \label{lem:monomial_smooth}
  Let $p \geq 0$.
  The monomial function $x \mapsto x^p$ belongs in $\smooth$. Furthermore,
  for any integer $m \geq 0$, for any compact set $K$ of $\R$,
  if $K+ := \sup_{x \in K} |x|$, then
  \begin{equation*}
    \|x \mapsto x^p\|_{C^m(K)}
    \leq \max(p,1)^m \max (1, K_+)^p.
  \end{equation*}
\end{lemma}

\begin{proof}
  The regularity is well-known.
  Let $x \in K$ and $0 \leq k \leq m$ an integer.
  Then,
  the $k$-th derivative of the monomial at $x$ is given by
  $p(p-1) \ldots (p-k+1) x^{p-k}$ if $p\geq k$ and $0$ otherwise.
  In both cases,
  this is smaller in absolute value
  than $\max (p,1)^k \max(K_+,1)^p$ which is smaller than $\max(p,1)^m \max(K_+,1)^p$.
\end{proof}

\begin{definition}
  \label{def:moment}
  \uses{def:compactly_supported_distribution,lem:monomial_smooth}
  Let $\nu \in \csdistrib$.
  For $p \in \N$, we define the $p$-th moment $\nu_p := \nu(x \mapsto x^p)$.
\end{definition}

\begin{definition}
  \label{def:radius_csd}
  \uses{def:moment}
  Let $\nu \in \csdistrib$.
  We define $$\rho(\nu) := \limsup_{p \to \infty} |\nu_p|^{1/p} .$$
\end{definition}

\begin{lemma}
  \label{lem:radius_finite}
  \uses{def:radius_csd}
  Let $\nu \in \csdistrib$.
  Then $\rho(\nu) < \infty$.
\end{lemma}

\begin{proof}
  By Lemma \ref{lem:extension_csd}, there exists a compact set $K$,
  a constant $C$ and an integer $m$
  such that, for all $h \in \smooth$,
  $|\nu(h)| \leq C \|h\|_{C^m(K)}$.
Let $p \geq 0$ be an integer.
Then by Lemma \ref{lem:monomial_smooth}, if $K_+ := \sup_{x \in K} |x|$,
$$|\nu_p| \leq C \max(p,1)^m \max (K_+,1)^p$$
and hence $(|\nu_p|^{1/p})_{p \geq 0}$ is bounded.
\end{proof}

\begin{proposition}
  \label{prop:Stieltjes_expansion}
  \notready
  \uses{lem:radius_finite,def:Stieltjes}
  Let $\nu \in \csdistrib$.
  There exists $M > 0$ such that $z \mapsto -\frac{1}{2 i \pi} \sum_{p=0}^\infty \frac{\nu_p}{z^{p+1}}$
  is an analytic extension of $F_\nu$ in $\{|z| > M\}$.
\end{proposition}

\begin{proof}
  Let $K$, $c$, $m$ be such that $|\nu(h)| \leq c \|h\|_{C^m([-K,K])}$ for all $h \in \smooth$.
  Let $N \geq 0$, $z \neq 0$. By linearity,
  \begin{equation*}
    -\frac{1}{2i \pi}
    \sum_{p=0}^N \frac{\nu_p}{z^{p+1}}
    = -\frac{1}{2 i \pi z} \nu \left( \sum_{p=0}^N \left(\frac{x}{z}\right)^p \right).
  \end{equation*}
  We need to prove that for $z \notin \R$
  large enough, $\sum_{p=0}^N \left(\frac{x}{z}\right)^p$
  converges to $\frac{1}{1-x/z}$ w.r.t. $\|\cdot\|_{C^m([-K,K])}$,
  which then implies that the above quantity converges to $F_\nu(z)$.
    [todo write the details]
\end{proof}

The main result of this section is as follows.

\begin{theorem}
  \label{thm:support_limsup}
  \notready
  \uses{thm:Stieltjes_holomorphic,prop:Stieltjes_expansion}
  Let $\nu \in \csdistrib$.
  Then $\supp \nu \subseteq [-\rho(\nu), \rho(\nu)]$.
\end{theorem}

\begin{proof}
  As in \cite[Lemma 4.9]{chen2025}.
\end{proof}
