% In this file you should put the actual content of the blueprint.
% It will be used both by the web and the print version.
% It should *not* include the \begin{document}
%
% If you want to split the blueprint content into several files then
% the current file can be a simple sequence of \input. Otherwise It
% can start with a \section or \chapter for instance.

\chapter{Random regular graphs}

In this chapter, we introduce the definitions related to random regular graphs and their spectrum.
We refer the reader to \cite{chung1992} for a more detailed introduction and motivations.

\section{Definition of a graph}

In this section, we define a few simple notions of graph theory, to set conventions.

As in \mathlibok{Graph}, a \emph{graph} is a pair $G = (V, E)$ where $V$ is a set of vertices, and
$E$ a set of edges, and each edge links two unordered, possibly identical vertices.

Note that this definition allows for loops (i.e. edges going from one vertex to itself) and
multi-edges (i.e. multiple edges connecting two vertices). This convention is essential to the proof
we are aiming for, which is why we use \mathlibok{Graph} instead of the much better-developed
\mathlibok{SimpleGraph}.

Following \mathlibok{Inc}, we say an edge $e$ is \emph{incident} to a vertex $x$ if there exists a
vertex $y$ such that $e$ links $x$ and $y$. As \mathlibok{IsLoopAt}, an edge is a \emph{loop} based
at a vertex $x$ if it links the vertex $x$ to itself.

\section{Finiteness, degree and regularity}

Let us now focus on the degree of vertices and regularity. We make definitions with minimal
hypotheses as these are fundamental objects.

\begin{definition}
  \label{def:locally_finite_at}
  \lean{LocallyFiniteAt}
  \uses{def:incidence}
  Let $G$ be a graph and $x$ be a vertex of $G$.
  We say $G$ is \emph{locally finite at $x$} if $x$ has a finite number of incident edges.
\end{definition}

\begin{definition}
  \label{def:degree}
  \lean{degree}
  \uses{def:incidence, def:loop, def:locally_finite_at}
  Let $G$ be a graph and $x$ be a vertex of $G$. We assume $G$ is locally finite at $x$.
  The \emph{degree} of $x$ is the number of incident edges, counting loops twice:
  \begin{equation*}
    \mathrm{deg}(x) = \# \{\text{edges incident to } x\}
    + \# \{ \text{loops based at } x\}.
  \end{equation*}
\end{definition}

\begin{proof}
  The set of loops at $x$ is included in the incidence set of $x$ by IsLoopAt.inc. Hence, if $G$ is
  locally finite at $x$, then $x$ has a finite number of loops and the degree is well-defined.
\end{proof}

\begin{definition}
  \label{def:locally_finite}
  \lean{LocallyFinite}
  \uses{def:locally_finite_at}
  A graph is said to be locally finite if it is locally finite at every vertex.
\end{definition}

\begin{definition}
  \label{def:regular}
  \lean{IsRegularOfDegree}
  \uses{def:locally_finite, def:degree}
  Let $d$ be a non-negative integer.
  Let $G$ be a locally finite graph.
  We say $G$ is regular of degree $d$ if every vertex of $G$ has degree $d$.
\end{definition}

We now conclude with the definition of a finite graph.

\begin{definition}
  \label{def:finite}
  \lean{Finite}
  \uses{def:locally_finite}
  A graph is \emph{finite} if its set of vertices is finite and it is locally finite.
\end{definition}

\section{Adjacency matrix}



\section{Random regular graphs: the permutation model}

In the rest of this blueprint, $N$ is a positive integer, and $[N] = \{1, \ldots, N\}$.
We also fix an even positive integer $d = 2r$.

\begin{definition}
  We denote as $\mathbf{S}_N$ the set of permutations of $[N]$, i.e. bijective maps $\sigma
  : [N] \rightarrow [N]$.
\end{definition}

\begin{lemma}
  The set $\mathbf{S}_N$ is finite and has cardinality $N!$.
\end{lemma}
We can therefore equip $\mathbf{S}_N$ with the uniform probability measure.

It will be more useful in what follows to view permutations as matrices.

\begin{definition}
  A square matrix is called a \emph{permutation matrix} if all of its entries are equal to $0$ or
  $1$, with exactly one $1$ on each row and column.
\end{definition}

\begin{lemma}
  Let $U$ be a permutation matrix. Then, $U$ is invertible and its inverse is the transpose $U^*$ of $U$.
\end{lemma}

\begin{definition}
  Let $\sigma \in \mathbf{S}_N$. We associate to $\sigma$ the $N \times N$ matrix
  $U_\sigma$ by letting, for each $i, j \in [N]$, $(U_\sigma)_{ij} = 1$ if $j = \sigma(i)$. [todo: check]
\end{definition}

\begin{lemma}
  The map $\sigma \mapsto U_\sigma$ is a bijection from $\mathbf{S}_N$ to the set of $N \times N$
  permutation matrices.
\end{lemma}

\section{The infinite $d$-regular tree}

\begin{definition}
  A \emph{walk} from $x$ to $y$ is a sequence of vertices and edges
  $x = v_0, e_1, v_1, \ldots, e_k, v_k = y$ such that for every $1 \leq j \leq k$, the edge $e_j$
  links the vertices $v_{j-1}$ and $v_j$. A walk is a \emph{path} if its edges are all distinct.
\end{definition}

\begin{definition}
  A graph $G$ is called a \emph{tree} if, for any pair of distinct vertices $x$, $y$, there exists
  one unique path from $x$ to $y$.
\end{definition}

[todo: define the infinite $d$-regular tree]


\chapter{Analytic tools}

Here we define some analytic prerequisites, following the structure of \cite[Section 4]{chen2025}.

\section{Spaces of functions and norms}

[todo: define $C^m[a,b]$ and the norm on it.]

\section{Markov inequalities}

\section{Chebyshev polynomials}

\section{Compactly supported distributions}

[todo: define a distribution and the notion of compactly supported distribution]
